---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw04pgnmergen613

<!-- badges: start -->
<!-- badges: end -->

The goal of hw04pgnmergen is to find the nth element of a recursive sequence,
and the sequence of which can be plotted using line graph.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gnmergen/hw04pgnmergen613")
```
## Example 1

Basic example of function myseq_n:

```{r example}
library(hw04pgnmergen613)
myseq_n(x = c(2,10,10), n = 5)
myseq_n(x = c(3,5,6), n = 10)

```

## Example 2
```{r}
my_data <- tibble::tribble(
 ~x, ~y, ~z, ~n,
2,4,3,3,
2,4,3,4,
2,4,3,5,
2,4,3,6,
2,4,3,7,
2,4,3,8,
2,4,3,9,
2,4,3,10,
2,4,3,12)

plotter(my_data)
```

Basic example of function plotter. We create a 4 column dataframe and utilizing
our function myseq_n the plotter will attempt to create a line graph of the 
generated sequency to the nth element.
